Conversations in time: interactive visualization to explore structured temporal data

### 2020-07-30 tsibbletalk.Rmd
minor tweaks

* Symbolic formula to express structural specifications among keyed units, using `/` and `*` from Wilkinson notation (10.2307/2346786) for nesting and crossing.
* Nesting variables generate hierarchical tree, hence `plotly_key_tree()`. Overview and navigation made easier.
* One-to-many linking: marking a single point of interest highlights all other points that share particular data values (connect-type)
* Lists of key values, and json
* R6 subclass of `SharedData` from {crosstalk}

@@

The {tsibbletalk} package provides a pair of UI and server functions, as a shiny module, to help with finding interesting time slices in a shiny application. The pair, `tsibbleDiceUI()` and `tsibbleDiceServer()`, presents a clean interface and forms a resusable piece. Like all shiny modules, users should supply a unique session id. The UI function `tsibbleDiceUI()` shows a slider that controls the number of periods, and a plot specified by users. The server function `tsibbleDiceServer()` is the workhorse, transforming data and updating the plot. It expects a `ggplot` (converted to `plotly` via `ggplotly()`) or `plotly` object. This plot can be line charts, or other graphical elements (such as boxplots). But it assumes that tsibble's time index is plotted on the x-axis. The other mandatory argument is to specify the number of seasonal periods that requires shifting.

* Transform and send newly-transformed data via server, without updating anything else (e.g. layout and graphical elements), to avoid completely redrawing. Performance.
* Double dispatch

>>>>

* Symbolic formula to express structural specifications among keyed units, using `/` and `*` from Wilkinson notation (10.2307/2346786) for nesting and crossing.
* Nesting variables generate hierarchical tree, hence `plotly_key_tree()`. Overview and navigation made easier.
* One-to-many linking: marking a single point of interest highlights all other points that share particular data values (categorical linking)
* Lists of key values, and json
* R6 subclass of mutaframes `SharedData` from {crosstalk} with metadata attached
* Self-linking: a single data source

@@

The {tsibbletalk} package provides a pair of UI and server functions, as a shiny module, to help with finding interesting time slices in a shiny application. The pair, decoupled to `tsibbleDiceUI()` and `tsibbleDiceServer()`, presents a clean interface and forms a resusable piece. Like all shiny modules, users should supply a unique session id. The UI function `tsibbleDiceUI()` shows a slider that controls the number of periods, and a plot specified by users. The server function `tsibbleDiceServer()` is the workhorse, transforming data and updating the plot. It expects a `ggplot` (converted to `plotly` via `ggplotly()`) or `plotly` object. This plot can be line charts, or other graphical elements (such as boxplots). But it assumes that tsibble's time index is plotted on the x-axis. The other mandatory argument is to specify the number of seasonal periods that requires shifting.

(Data flows) Transformed data generally requires redrawing the plot, and worsen the performance of shiny. The underlying tsibble data is called back and transformed in R. Using the `plotly.js` react method, only transformed data is sent to the server side, while keeping the rest configuration unchanged (e.g. layout and graphical elements). It is performant, and users will not experience notable delay in response to the change in the slider input. Dissect time index, and propagate transformed data to shiny server.

### 2020-07-30 tsibbletalk.tex
minor tweaks

\begin{itemize}
\tightlist
\item
  Symbolic formula to express structural specifications among keyed
  units, using \texttt{/} and \texttt{*} from Wilkinson notation
  (10.2307/2346786) for nesting and crossing.
\item
  Nesting variables generate hierarchical tree, hence
  \texttt{plotly\_key\_tree()}. Overview and navigation made easier.
\item
  One-to-many linking: marking a single point of interest highlights all
  other points that share particular data values (connect-type)
\item
  Lists of key values, and json
\item
  R6 subclass of \texttt{SharedData} from \{crosstalk\}
\end{itemize}

@@

The \{tsibbletalk\} package provides a pair of UI and server functions,
as a shiny module, to help with finding interesting time slices in a
shiny application. The pair, \texttt{tsibbleDiceUI()} and
\texttt{tsibbleDiceServer()}, presents a clean interface and forms a
resusable piece. Like all shiny modules, users should supply a unique
session id. The UI function \texttt{tsibbleDiceUI()} shows a slider that
controls the number of periods, and a plot specified by users. The
server function \texttt{tsibbleDiceServer()} is the workhorse,
transforming data and updating the plot. It expects a \texttt{ggplot}
(converted to \texttt{plotly} via \texttt{ggplotly()}) or
\texttt{plotly} object. This plot can be line charts, or other graphical
elements (such as boxplots). But it assumes that tsibble's time index is
plotted on the x-axis. The other mandatory argument is to specify the
number of seasonal periods that requires shifting.

\begin{itemize}
\tightlist
\item
  Transform and send newly-transformed data via server, without updating
  anything else (e.g.~layout and graphical elements), to avoid
  completely redrawing. Performance.
\item
  Double dispatch
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  Symbolic formula to express structural specifications among keyed
  units, using \texttt{/} and \texttt{*} from Wilkinson notation
  (10.2307/2346786) for nesting and crossing.
\item
  Nesting variables generate hierarchical tree, hence
  \texttt{plotly\_key\_tree()}. Overview and navigation made easier.
\item
  One-to-many linking: marking a single point of interest highlights all
  other points that share particular data values (categorical linking)
\item
  Lists of key values, and json
\item
  R6 subclass of mutaframes \texttt{SharedData} from \{crosstalk\} with
  metadata attached
\item
  Self-linking: a single data source
\end{itemize}

@@

The \{tsibbletalk\} package provides a pair of UI and server functions,
as a shiny module, to help with finding interesting time slices in a
shiny application. The pair, decoupled to \texttt{tsibbleDiceUI()} and
\texttt{tsibbleDiceServer()}, presents a clean interface and forms a
resusable piece. Like all shiny modules, users should supply a unique
session id. The UI function \texttt{tsibbleDiceUI()} shows a slider that
controls the number of periods, and a plot specified by users. The
server function \texttt{tsibbleDiceServer()} is the workhorse,
transforming data and updating the plot. It expects a \texttt{ggplot}
(converted to \texttt{plotly} via \texttt{ggplotly()}) or
\texttt{plotly} object. This plot can be line charts, or other graphical
elements (such as boxplots). But it assumes that tsibble's time index is
plotted on the x-axis. The other mandatory argument is to specify the
number of seasonal periods that requires shifting.

(Data flows) Transformed data generally requires redrawing the plot, and
worsen the performance of shiny. The underlying tsibble data is called
back and transformed in R. Using the \texttt{plotly.js} react method,
only transformed data is sent to the server side, while keeping the rest
configuration unchanged (e.g.~layout and graphical elements). It is
performant, and users will not experience notable delay in response to
the change in the slider input. Dissect time index, and propagate
transformed data to shiny server.
